Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-13 main.tex
Temporal sections.

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
\newcommand{\TW}{\triangleright}

@@

We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.

@@

In this paper, we design $\lambda^{\textrm{MD}}$ by introducing dependent type into $\lambda^{\TW\%}$.
You can make more efficient programs from existing dependent typed programs with $\lambda^{\textrm{MD}}$.

@@

\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
\end{abstract}

\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

>>>>

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
\newcommand{\TW}{\triangleright}
\newcommand{\LTP}{$\lambda^{\triangleright\%}$}
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$}
\newcommand{\LLF}{$\lambda^{\textrm{LF}}$}

@@

We develop yet another typed multi-stage calculus \LMD.
It extends Hanada and Igarashi's \LTP with dependent type.

@@

In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
You can make more efficient programs from existing dependent typed programs with \LMD.

@@

\keywords{Multistage programming \and Dependent type}
\end{abstract}

\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Dependent Types}
\subsection{Multi-Stage Calculus}
\subsection{Organaization of the Paper}
\section{Informal Overview of \LMD}
\subsection{\LLF}
\subsection{\LTP}
\section{Formal Definition of \LMD}
\subsection{Kinding Rules}
\subsection{Equivalence Rules}
\section{First Section}
\section{Related Work}
\section{Conclusions}

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.
